\begin{thebibliography}{}
    
\bibitem{sheknar2017foil}
R. Shekhar, S. Pezzelle, Y. Klimovich, A. Herbelot, M. Nabi, E. Sangineto, and R. Bernardi. FOIL it! find one mismatch between image and language caption. In Proceedings of the 55th Annual Meeting of the Association for Computational Linguistics (Volume 1: Long Papers), pp. 255–265, Vancouver, Canada, July 2017b. Association for Computational Linguistics.

\bibitem{kesen2023ViLMA}
I. Kesen, A. Pedrotti, M. Dogan, M. Cafagna, E. Can Acikgoz, L. Parcalabescu, I. Calixto, A. Frank, A. Gatt, A. Erdem, E. Erdem.
ViLMA: A Zero-Shot Benchmark for Linguistic and Temporal Grounding in Video-Language Models.
arXiv:2311.07022.

\bibitem{lei2021clipbert}
J. Lei et al., "Less is More: CLIPBERT for Video-and-Language Learning via Sparse Sampling," 2021 IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR), Nashville, TN, USA, 2021, pp. 7327-7337, doi: 10.1109/CVPR46437.2021.00725.

\bibitem{jei2022}
J. Lei, T. L. Berg, and M. Bansal. Revealing single frame bias for video-and-language learning. arXiv:2206.03428, 2022.

\bibitem{zhu2022pretraining}
X. Zhu, J. Zhu, H. Li, X. Wu, H. Li, X. Wang, and J. Dai. Uni-perceiver: Pre-training unified architecture for generic perception for zero-shot and few-shot tasks. In Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR), pp. 16804–16815, June 2022.

%\bibitem{Buchen-Mainardi 1975}
%P.W. Buchen, F. Mainardi,Asymptotic expansions for transient viscoelastic waves, {\it Journal de M{\'e}canique} {14},  597--608 (1975).

%\bibitem{AG-FM_MECC16}
%A. Giusti, F. Mainardi, A dynamic viscoelastic analogy for fluid-filled elastic tubes, {\it Mecanica}, published on line, 04 February  2016.(2015).
\end{thebibliography}
